Does Anybody Really Know What Time It Is?\\ Automating the Extraction of Date Scalars

### 2015-07-13 nlp.tex
some math notation added.

In the context of CFGs, probabilities have been used to define a probability distribution over a set of parse trees defined by the CFG, and are a useful method for modeling such ambiguity~\cite{Collins:2003,Manning:1999}. The resulting formalism called Probabilistic Context-Free Grammar (PCFG), extends the CFG by assigning probabilities to the production rules of the grammar. During the process of parsing the date-time pattern, the probabilities are used as a filtering mechanism to rank the pattern(s) that a given string resolves to in the grammar. The parser then chooses the parse tree with the maximum probability.

@@

\subsection{Parsing the PCFG}
Given a date-time string $s$, as input, we determine the highest scoring parse tree $t$ as  $max_{t \in T(s)} p(t)$.

>>>>

In the context of CFGs, probabilities have been used to define a probability distribution over a set of parse trees defined by the CFG, and are a useful method for modeling such ambiguity~\cite{Collins:2003,Manning:1999}. The resulting formalism called Probabilistic Context-Free Grammar (PCFG), extends the CFG by assigning probabilities to the production rules of the grammar. During the process of parsing the date-time pattern, the probabilities are used as a filtering mechanism to rank the pattern(s) that a given string resolves to in the grammar.

Given a CFG grammar $G$, we define  $\tau_G(s)$ as the set of all possible parse trees for input date-time string $s$.  For any $t \in \tau(G)$, the probability $p(t) \ge 1$. In addition, $\sum_{t \in \tau_{G}} = 1$. The parser then chooses the parse tree with the maximum probability, \textit{i.e.} given a date-time string $s$, as input, we determine the highest scoring parse tree $t$ as  $max_{t \in \tau(s)} p(t)$.

@@

\subsection{Parsing the PCFG}
